Resource Buying Games

### 2017-01-05 slides.tex
added slide on matroid operations
added cuts to matroids
added player 2 part of shared graph

\documentclass{beamer}
\usepackage{pgfplots}
\usepackage{tikz}
\usetheme{metropolis}
\title{Resource Buying Games}
\author[C. Welzel]{Christoph Welzel}

\newcommand{\tupel}[1]{\left(#1\right)}
\newcommand{\set}[1]{\left{#1\right}}

\begin{document}
\maketitle
\section{Introduction}
\begin{frame}
  % \begin{itemize}
  %   \item Context (1 slide)
  %     \begin{itemize}
  %       \item What is modelled?
  %       \item How is it modelled?
  %     \end{itemize}
  %   \item Example (1 slide)
  %     \begin{itemize}
  %       \item Introducing an example which is used to illustrate different
  %         aspects throughout the presentation
  %       \item Interleaved graphs for two players, both want to acquire a
  %         spanning tree
  %     \end{itemize}
  % \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Definition: Matroid}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{equation*}
      M = (E, B)
    \end{equation*}
    \vspace{-0.8cm}
    \begin{itemize}
      \item $E$: ground-set
      \item $B$: set of bases
      \item \emph{basis exchange property}:
        \vspace{-1cm}
        \begin{center}
          \begin{align*}
            \forall &X, Y\in B:\\
            &\forall x\in (X\setminus Y)\\
            &\exists y\in (Y\setminus X):\\
            &\;(X\setminus \{x\})\cup\{y\}\in B
          \end{align*}
        \end{center}
    \end{itemize}
    \column{0.5\textwidth}
  \end{columns}
\end{frame}

\subsection{Pure Nash equilibria}
\begin{frame}
  % \begin{itemize}
  %   \item (1 slide)
  %   \item Explain what PNEs are (maybe from previous presentations this
  %     knowledge can be assumed)
  %   \item Again the example can be used to illustrate what uniliteral change
  %     might imply
  % \end{itemize}
% \end{frame}
% \subsection{Basic matroid theory}
% \begin{frame}
  % \begin{itemize}
  %   \item (2/3 slides)
  %   \item Formally define matroids
  %   \item Explain the meaning of the definition by using the example
  %   \item Contraction and deletion (again with example)
  %   \item Define Matroid games (and mention that the example fits)
  % \end{itemize}
\end{frame}

\section{Algorithm: PNE in Unweighted Matroid Games}
\subsection{Algorithm}
\begin{frame}
  % \begin{itemize}
  %   \item Present algorithm (2 slides)
  %   \item Execute one or two steps at example (only a slide but animation might
  %     take some time ca. 5 minutes)
  % \end{itemize}
\end{frame}

>>>>

\documentclass{beamer}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{csquotes}
\usetheme{metropolis}
\title{Resource Buying Games}
\author[C. Welzel]{Christoph Welzel}

\newcommand{\tupel}[1]{\left(#1\right)}
\newcommand{\set}[1]{\left\{#1\right\}}

\begin{document}
\input{tikz/settings}
\maketitle
\section{Introduction}
\begin{frame}
  % \begin{itemize}
  %   \item Context (1 slide)
  %     \begin{itemize}
  %       \item What is modelled?
  %       \item How is it modelled?
  %     \end{itemize}
  %   \item Example (1 slide)
  %     \begin{itemize}
  %       \item Introducing an example which is used to illustrate different
  %         aspects throughout the presentation
  %       \item Interleaved graphs for two players, both want to acquire a
  %         spanning tree
  %     \end{itemize}
  % \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Definition: Matroid}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{equation*}
      M = (E, B)
    \end{equation*}
    \vspace{-0.8cm}
    \begin{itemize}
      \item $E$: ground-set
      \item $B$: set of bases
      \item \emph{basis exchange property}:
        \vspace{-1cm}
        \begin{center}
          \begin{align*}
            \forall &X, Y\in B:\\
            &\forall x\in (X\setminus Y)\\
            &\exists y\in (Y\setminus X):\\
            &\;(X\setminus \set{x})\cup\{y\}\in B
          \end{align*}
        \end{center}
    \end{itemize}
    \column{0.5\textwidth}
    \uncover<2->{Spanning trees:}
    \begin{center}
      \uncover<2->{\resizebox{0.8\textwidth}{!}{\input{tikz/graphp1}}\\[0.5cm]}
      \uncover<3->{\resizebox{0.4\textwidth}{!}{\input{tikz/graphp1S1}}}
      \uncover<4->{\resizebox{0.4\textwidth}{!}{\input{tikz/graphp1S2}}}
      \uncover<5->{\resizebox{0.4\textwidth}{!}{\input{tikz/graphp1S3}}}
    \end{center}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Operations on Matroids $\mathcal{M} = \tupel{E, \mathcal{B}}$}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{center}
      Contraction:
    \end{center}
    \vspace{-0.6cm}
    \begin{align*}
      &\mathcal{M}/e = \tupel{E\setminus\set{e}, \mathcal{B}/e}\text{ with}\\
      &\mathcal{B}/e = \set{B\subseteq (E\setminus\set{e})\middle| B\cup\set{e}\in\mathcal{B}}
    \end{align*}
    \column<4->{0.5\textwidth}
    \begin{center}
      Deletion:
    \end{center}
    \vspace{-0.6cm}
    \begin{align*}
      &\mathcal{M}\setminus e = \tupel{E\setminus\set{e},\mathcal{B}\setminus e}\text{ with}\\
      &\mathcal{B}\setminus e = \set{B\subseteq E\setminus\set{e}\middle|B\in\mathcal{B}}
    \end{align*}
  \end{columns}
  \begin{center}
    \begin{tikzpicture}
      \uncover<2->{\node (G) {\input{tikz/graphp1}};
      \node[right=1 of G] (leadsto) {\Huge$\leadsto$};}
      \uncover<3>{\node[right=1 of leadsto] (G') {\input{tikz/graphp1Cont}};}
      \uncover<5>{\node[right=1 of leadsto] (G'') {\input{tikz/graphp1Del}};}
    \end{tikzpicture}
  \end{center}
\end{frame}

\begin{frame}
  \frametitle{Cuts in Matroids}
  \begin{columns}
    \column{0.7\textwidth}
    $\mathcal{M} = \tupel{E, \mathcal{B}}$
    \begin{itemize}
      \item \emph{Cut}: inclusion-wise minimal $C\subseteq E$ such that
        $E\setminus C$ does not contain a basis of $\mathcal{M}$
      \item[$\leadsto$] $\mathcal{C}\tupel{\mathcal{M}} =
        \set{C\subseteq E\middle| C\text{ is a cut in } \mathcal{M}}$
    \end{itemize}
    \column{0.3\textwidth}
    \resizebox{0.8\textwidth}{!}{\input{tikz/graphp1}}
  \end{columns}
  \vspace{0.7cm}
  \begin{columns}
    \column{0.33\textwidth}
    \uncover<2->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut1}}\\[0.3cm]}
    \uncover<3->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut2}}}
    \column{0.33\textwidth}
    \uncover<4->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut3}}}\\[0.3cm]
    \uncover<5->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut4}}}
    \column{0.33\textwidth}
    \uncover<6->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut5}}}
  \end{columns}
\end{frame}

\section{Algorithm: PNE in Unweighted Matroid Games}
\subsection{Algorithm}
\begin{frame}
  \frametitle{Algorithm}
  \begin{tabular}{|lll|}
    \hline
    (i) & Init: &\hspace{-0.6cm}\parbox{0.8\textwidth}{
        \begin{itemize}
          \item \parbox{0.7\textwidth}{every player: empty working basis, complete ground-set, complete set of valid result bases}
          \item every resource: cost for next load, current load
        \end{itemize}
      }\\\hline
    (ii) & Find: &\hspace{-0.6cm}\parbox{0.8\textwidth}{
        \begin{itemize}
          \item inclusion-min (necessary cost)-max cut $C$
          \item minimal cost resource $e$ in $C$
          \item owner $i$ of $C$
        \end{itemize}
      }\\\hline
    (iii) & Pick: &\hspace{-0.6cm}\parbox{0.8\textwidth}{
        \begin{itemize}
          \item $i$: add $e$ to working basis, contract matroid to $e$
          \item $e$: update marginal cost and increase load
          \item all player: delete elements $C\setminus\set{e}$ from matroid
        \end{itemize}
      }\\\hline
    (iv) & Break: &\hspace{-0.6cm}\parbox{0.8\textwidth}{
        \begin{itemize}
          \item exists player with incomplete basis: goto (ii)
          \item otherwise: return chosen bases and payments
        \end{itemize}
      }\\\hline
  \end{tabular}
\end{frame}

\begin{frame}
  \frametitle{Example: Graph}
  \resizebox{\textwidth}{!}{\input{tikz/graphp2}}
\end{frame}
